Safe Transferable Regions

### 2016-10-03 paper/typeinference-proofs.tex
switched to ESOP formatting

@@

>>>>

Invariants and other points:
\begin{itemize}
  \item Every predicate variable has a single domain-constraint.
  \item Progress: Every region-variable will be unified with some constant.
  \item Notation: should we use a different notation to distinguish a validity constraint
    from actual entailment?
\end{itemize}

@@

\begin{lemma}
  Consider any constraint satisfying the above invariant with a rhs of the
  form $\pi_i \outlives \pi_j$, with both $\pi_i$ and $\pi_j$ region constants.
  (a) If $\{ \pi_i, \pi_j \} \subseteq \predDeltaMap(\varphi)$,
  then $\isvalid{\varphi}{\pi_i \outlives \pi_j}$ in any solution to the constraints.
  (b) If $\{ \pi_i, \pi_j \} \not \subseteq \predDeltaMap(\varphi)$,
  then $\isvalid{\phicx}{\pi_i \outlives \pi_j}$ in any solution to the constraints.
\end{lemma}
